\documentclass[12pt,a4paper]{report}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{titlesec}

\onehalfspacing
\pagestyle{fancy}
\fancyhead{}
\fancyfoot{}
\fancyfoot[C]{\thepage}
\titleformat{\chapter}[display]{\bfseries\Large}{Chapter \thechapter}{1ex}{\Large}

\begin{document}
\begin{titlepage}
    \centering
    \vspace*{1in}
    {\Large \textbf{Library Management System for Ethiopian Universities}}\\[1em]
    {Graduation Project Documentation}\\[2em]
    {Prepared by: Your Name Here}\\[1em]
    {Supervisor: Advisor Name}\\[2em]
    {Department of Computer Science}\\[1em]
    {November 2025}
\end{titlepage}

\chapter*{Abstract}
Summarize the project motivation, objectives, methodology, and key results in 250-300 words.

\chapter*{Acknowledgements}
Acknowledge academic advisors, department, family, and contributors.

\tableofcontents
\listoffigures
\listoftables

\chapter{Introduction}
\section{Background of the Study}
Discuss digital transformation initiatives in Ethiopian universities and current library challenges.

\section{Problem Statement}
Present the gaps identified in manual library processes.

\section{Objectives}
List general and specific objectives of the study.

\section{Scope and Limitations}
Define coverage of the project.

\section{Significance of the Study}
Explain benefits to stakeholders.

\chapter{Literature Review}
Provide theoretical and empirical review of Library Management Systems, focusing on local context.

\chapter{Methodology}
Describe requirement gathering, analysis, and design methods.

\chapter{System Design and Implementation}
Detail architecture, database schema, and UI design.

\chapter{Testing and Discussion}
Summarize testing strategy, cases, and results.

\chapter{Conclusion and Recommendations}
Present conclusions, recommendations, and future work.

\appendix
\chapter{Appendix}
Include questionnaires, test cases, and user manuals.

\end{document}
